Adversarial State Aggregation

### 2019-12-30 minutia/paper/paper.tex
updated paper

    \begin{equation}
        \hat{p}_{x y}(u)=\sum_{j=1}^{n} p_{x j}(u) \phi_{j y},
    \end{equation}

    where $p_ {x j}$ is the transition probabilities from a representative state, $x$, to an original state, $j$
    and $\phi_{j y}$ is the aggregation probabilities from an original state, $j$, to a representative state, $y$.
    The rewards are defined as:

    \begin{equation}
        \hat{g}(x, u)=\sum_{j=1}^{n} p_{x j}(u) g(x, u, j)
    \end{equation}

@@

    We developed an aggregation scheme to lower the state space dimensionality by assigning same action to the state
    in a neighbourhood, so called nearest neighbour/ piecewise linear aggregation.

>>>>

    \begin{equation}
        \hat{P}_{s s^\prime}(a)=\sum_{j=1}^{n} P_{s j}(a) \phi_{j y},
    \end{equation}

    where $p_ {s j}$ is the transition probabilities from a representative state, $s$, to an original state, $j$
    and $\phi_{j s^\prime}$ is the aggregation probabilities from an original state, $j$, to a representative state,
    $s^\prime$.
    The rewards are defined as:

    \begin{equation}
        \hat{r}(s, a)=\sum_{j=1}^{n} P_{s j}(a) r(s, a, j),
    \end{equation}

    where $\hat{r}(s, a)$ is the received reward at state $s$ by taking action $a$.

    Aggregation then helps us to derive the value function.
    Approximated optimal value function is a weighted sum of optimal rewards and can be computed by
    equation\ref{approx val func} where $r_{s^\prime}^{\ast}$ is optimal reward at represented state $s$.

    \begin{equation} \label{approx val func}
        \tilde{V}(j)=\sum_{s^\prime \in \mathcal{U}} \phi_{j s^\prime} r_{s^\prime}^{\ast},
    \end{equation}

    In this paper, we lay down the aggregation framework and then solve the aggregate problem by a tabular method
    such as value iteration (VI), policy iteration (PI).

@@

    We developed an aggregation scheme to lower the state space dimensionality by assigning same action to the state
    in a neighbourhood, so called nearest neighbour/ piecewise linear aggregation.
    We then solve directly the lower dimension problem which relatively takes less computation.
